\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-16 article.tex
fix second part

The directivity in the network introduce causal relations through neurons. A
directed edge, i.e. $a_{i,j} = 1$ and $a_{j,i} = 0$, means that neuron $i$
causes $j$. The causal mechanism implies that when neuron $i$ is active, also
denoted in this paper as a firing event or a burst, neuron $j$ may be
afterwards activated consequently. Let us notice that neuron $j$ depends on
all its ancestors and its activation may not be as straightforward as we may
think if the causal is not systematic (stochastic?). The reciprocal
phenomenon is only possible when the edge is bidirectionnal, i.e. $a_{i,j} =
a_{j,i} = 1$.

>>>>

The directivity in the network introduce causal relations through neurons. A
directed edge, i.e. $a_{i,j} = 1$ and $a_{j,i} = 0$, means that neuron $i$
causes $j$. The causal mechanism implies that when neuron $i$ is active, also
denoted in this paper as a firing event or a burst, neuron $j$ may be
afterwards activated consequently. Let us notice that neuron $j$ depends on
all its ancestors and its activation may not be as straightforward as we may
think if the causal activation is not systematic (stochastic?). The reciprocal
phenomenon is only possible when the edge is bidirectionnal, i.e. $a_{i,j} =
a_{j,i} = 1$.
